\section{Introduction}

\Idris{} is a functional programming language with full dependent
types. It has been designed and developed with an emphasis on
\emph{systems} programming --- to this end, from the start we have
taken efficiency and interaction with the outside world seriously. 

[What can we do now that we couldn't before? Generic programming,
  lightweight verification of low level systems code. Real
  applications which interact with the outside world.]

What does it mean to be ``practical''? Or ``efficient''?

Practical --- interaction with operating systems, web browsers,
etc. Can we run ``Real World'' programs? Can we ``tackle the awkward
squad''? We evaluate this qualitatively by implementing a web
application framework with safety guarantees enforced by the type
system.

Efficient --- are the resulting applications comparable with those
written in more mainstream languages (Java, C, etc are considered
``fast enough'', even Python, Perl, or Haskell. Is there anything in
DTP which gets in the way of this?) It is hard to compare languages
fairly for efficiency, but we attempt to do so by... [comparing
  application performance?]

\subsection{Dependent Types}

Definition and brief example.

\subsection{Contributions}

What do we learn from developing applications in a language with full
dependent types (as opposed to, say, theorem proving, or using more
restricted forms such as GADTs?).

Programming techniques developed in the context of DTP (e.g. views,
generic programming, verified EDSLs) can be relevant for real world
applications, in that they give new abstractions and improve
confidence in correctness. [Demonstrate by writing one and making
  claims about correctness].

We identify essential features of a compiler for a dependently typed
language. [Demonstrate they are essential by measuring performance
  of real application with and without.]

By developing an application, exploting dependent types where
appropriate, we identify common dependently typed programming idioms.
